Solar and other renewable power sources are becoming an integral part
of the electrical grid in the United States.
In the Southwest US, solar and wind power plants already serve over 20\%
of the electrical load during the daytime on sunny days in the Spring.
While solar power produces fewer emissions and has a lower carbon
footprint than burning fossil fuels, solar power is only generated
during the daytime and it is variable due to clouds blocking the sun.
Electric utilities that are required to maintain a reliable
electricity supply benefit from anticipating the schedule of power
output from solar power plants.
Forecasting the irradiance reaching the ground, the primary input to a
solar power forecast, can help utilities understand and respond to the
variability.
This dissertation will explore techniques to forecast irradiance that
make use of data from a network of sensors deployed throughout Tucson,
AZ.
The design and deployment of inexpensive sensors used in the network
will be described.
We will present a forecasting technique that uses data from the
sensor network and outperforms a reference persistence forecast for
one minute to two hours in the future.
We will analyze the errors of this technique in depth and suggest ways
to interpret these errors.
Then, we will describe a data assimilation technique, optimal
interpolation, that combines estimates of irradiance derived from
satellite images with data from the sensor network to improve the
satellite estimates.
These improved satellite estimates form the base of future work that will
explore generating forecasts while continuously assimilating new data.

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "dissertation"
%%% End:
