This dissertation would not have been possible without the support of
numerous individuals and institutions.
I would first like to thank my dissertation director, Alex Cronin for
his guidance and insightful questions.
My co-advisor, Matti Morzfeld, helped shape the second half of this
dissertation and was always ready with practical advice.
I would also like to thank my third committee member, B.G. Potter, for
his time and ideas.

I worked closely with Will Holmgren who provided numerous edits,
ideas, and set a high standard.
Ardeth Barnhart and the UA Renewable Energy Network (now Institute of
Energy Solutions) provided financial support and helped keep our group
connected with the utilities.
Mike Eklund and Rey Granillo were helpful in setting up and
maintaining the IT infrastructure necessary for the project.
I would also like to thank group members Eric Betterton and Mike
Leuthold for their support.
Adria Brooks, Dani DellaGiustina, and Tyler St.\ Germaine braved the
sun and helped install many of the irradiance sensors.
The studies of potential forecasting applications by Daniel Cormode
and Sophia Chen have been helpful.
Travis Harty and Leland Boeman have provided some interesting
conversations in the fish bowl.

This dissertation would not have been possible without the rooftop
solar power data provided by Technicians for Sustainability.
I would like to thank Tucson Electric Power for their initial and
continued support of this project.
I would also like to thank Arizona Public Service and Public Service
Company of New Mexico for supporting our group.
Finally, I would like to thank my family and friends for all their
constant support.



%%% Local Variables:
%%% mode: latex
%%% TeX-master: "dissertation"
%%% End:
