\chapter{LIST OF PUBLICATIONS CO-AUTHORED BY A. T. LORENZO}
Peer-reviewed publications:
\begin{enumerate}
% e.g. \item W.F. Holmgren, R. Trubko, I. Hromada, and A.D. Cronin, \emph{``Measurement of a Wavelength of Light for Which the Energy Shift for an Atom Vanishes"} Physical Review Letters {\bf109}, 243004, (2012).
\item A. T Lorenzo, M. Morzfeld, W. F. Holmgren, and A. D. Cronin,
  ``Optimal interpolation of satellite and ground data for
    irradiance nowcasting at city scales,'' \emph{Solar Energy},
    vol. 144, pp. 446--474, 2017.

\item A. T Lorenzo, W. F. Holmgren, A. D. Cronin, ``Irradiance
  forecasts based on an irradiance monitoring network, cloud motion,
  and spatial averaging,'' \emph{Solar Energy}, vol. 122,
  pp. 1158--1169, 2015.

\end{enumerate}



\noindent Presentations and posters:

\begin{enumerate}

\item American Meteorological Society Annual Meeting, 2017, Poster:
  ``nabu: A distributed, parallel, data processing platform,''
  A. T. Lorenzo and W. F. Holmgren.

\item American Meteorological Society Annual Meeting, 2017, Poster:
  ``An Open Source Solar Power Forecasting Tool Using PVLIB Python,''
  W. F. Holmgren, A. T. Lorenzo, and D. G. Groenendyk.

\item American Meteorological Society Annual Meeting, 2017, Poster:
  ``Utility Scale Solar and Wind Power Variability in the Southwest
  United States,''
  W. F. Holmgren and A. T. Lorenzo.

\item American Meteorological Society Annual Meeting, 2017, Poster:
  ``An Evaluation of Nine ARW-WRF Microphysics Schemes for Solar Power
  Forecast in Arizona,''
  Y. Cao, W. F. Holmgren, M. Leuthold, C. Castro, A. T. Lorenzo, and
  H. Chang.

\item American Geophysical Union Fall Meeting, 2016, Poster:
  ``Fusing Satellite-Derived Irradiance and Point Measurements through
  Optimal Interpolation,''
  A. T. Lorenzo, M. Morzfeld, W. F. Holmgren, and A. D. Cronin.

\item Arizona Student Energy Conference, 2016, Poster:
  ``Improving satellite-derived irradiance estimates using sparse
  rooftop solar data and optimal interpolation,''
  T. M. Harty, A. T. Lorenzo, M. Morzfeld, W. F. Holmgren, and
  A. D. Cronin.

\item IEEE Photovoltaics Specialists Conference, 2016, Talk:
  ``Optimal Interpolation of Satellite Derived Irradiance and Ground
  Data,''
  A. T. Lorenzo, M. Morzfeld, W. F. Holmgren, and A. D. Cronin.

\item Arizona Student Energy Conference, 2015, Talk:
  ``Operational Wind and Solar Power Forecasting in the Southwest,''
  A. T. Lorenzo, W. F. Holmgren, M. Leuthold, C. K. Kim, R. Granillo,
  E. A. Betterton, and A. Barnhart.

\item IEEE Photovoltaics Specialists Conference, 2015, Poster:
  ``PVLIB Python 2015,''
  W. F. Holmgren, R. W. Andrews, A. T. Lorenzo, and J. S. Stein.

\item American Meteorological Society Annual Meeting, 2015, Talk:
  ``U. Arizona Renewable Power Forecasting,''
  W. F. Holmgren, A. D. Cronin, A. T. Lorenzo, E. A. Betterton,
  M. Leuthold, C. K. Kim, A. Barnhart, and R. Granillo.

\item American Meteorological Society Annual Meeting, 2015, Poster:
  ``Intra-hour solar power forecast using a real-time irradiance
  monitoring network,''
  A. T. Lorenzo, W. F. Holmgren, M. Leuthold, C. K. Kim, A. D. Cronin,
  and E. A. Betterton.

\item IEEE Photovoltaics Specialists Conference, 2014, Talk:
  ``Short-Term PV Power Forecasts Based on a Real-Time Irradiance
  Monitoring Network,''
  A. T. Lorenzo, W. F. Holmgren, A. D. Cronin, E. A. Betterton,
  M. Leuthold, and C. K. Kim.

\item IEEE Photovoltaics Specialists Conference, 2014, Talk:
  ``Real-Time Renewable Power Forecasting,''
  W. F. Holmgren, A. D. Cronin, A. T. Lorenzo, E. A. Betterton,
  M. Leuthold, C. K. Kim, A. Barnhart, and R. Granillo.

\item IEEE Photovoltaics Specialists Conference, 2014, Talk:
  ``The economic value of forecasts for optimal curtailment strategies
  to comply with ramp rate rules,''
  D. Cormode, A. T. Lorenzo, W. F. Holmgren, S. Chen, and
  A. D. Cronin.

\item IEEE Photovoltaics Specialists Conference, 2013, Talk:
  ``Comparing ramp rates from large and small PV systems, and
  selection of batteries for ramp rate control,''
  D. Cormode, A. D. Cronin, W. Richardson, A. T. Lorenzo,
  A. E. Brooks, and D. N. Dellagiustina.

\end{enumerate}



%%% Local Variables:
%%% mode: latex
%%% TeX-master: "dissertation"
%%% End:
